---
title: "Statistical inference with the GSS data"
output: 
  html_document: 
    fig_height: 4
    highlight: pygments
    theme: spacelab
---

## Setup

### Load packages

```{r load-packages, message = FALSE}
library(dplyr)
library(ggplot2)
library(olsrr)
library(tidyr)
library(gplots)
```

### Load data

```{r load-data}
load("gss.Rdata")
```



* * *

## Part 1: Data

The data comes from the General Social Surveys conducted by the National Opinion Research Center using a standard questionaire.  Surveys were conducted in 1972, 1973, 1974, 1975, 1976, 1977, 1978, 1980, 1982, 1983, 1984, 1985, 1986, 1987, 1988, 1989, 1990, 1991, 1993, 1994, 1996, 1998, 2000, 2002, 2004, 2006, 2008, 2010, 2012, 2014, and 2016.  A total of 62466 interviews have been conducted, with the median length of the interview being about one and one-half hours.  

Surveys from 1972 through 2004 were independently drawn samples of English-speaking persons 18 years of age or over, living in non-institutional arrangements within the United States. Starting in 2006 Spanish-speakers were added to the target population. 

Until 2000, the survey was administered in a paper-and-pencil format, but starting in 2002, the GSS was conducted by computer-assisted personal interviewing (CAPI).

### Scope of Inference:

The data include a large number of randomly drawn responses, so it is generalizable to the target population of persons 18 years old or older living in non-institutional arrangements within the United States. 

This study is observational without random assignment, and therefore no causal relationships can be inferred from this data.  The length of the study might be a concern in that respondents may become fatigued with such a long questionaire and begin to give less accurate responses.

* * *

## Part 2: Research question

I'm interested in racial diversity issues particularly related to income inequality.  I'm curious to see if certain regions of the United States might correlate with higher incomes for people of color.  Therefore, my research question is:

Does the constant annual income (dollars adjusted for inflation) of respondents who self-idenfify as black differ significantly by region?


* * *

## Part 3: Exploratory data analysis

NOTE: Insert code chunks as needed by clicking on the "Insert a new code chunk" 
button (green button with orange arrow) above. Make sure that your code is visible
in the project you submit. Delete this note when before you submit your work.

* * *

## Part 4: Inference

NOTE: Insert code chunks as needed by clicking on the "Insert a new code chunk" 
button (green button with orange arrow) above. Make sure that your code is visible
in the project you submit. Delete this note when before you submit your work.